Paper Visualization

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
finished preliminary code

# Plot the bar graph showing the frequency of each quartile
ggplot(all_threads, aes(x = Quartile)) +
  geom_bar(fill = "skyblue", color = "black") +
  geom_text(stat='count', aes(label=..count..), vjust=-0.5) +  # Add labels above bars
  labs(title = "Frequency of Thread Relevancy Quartiles",
       x = "Quartile",
       y = "Frequency") +
  theme_minimal()

@@

# Plot the histogram with density overlay using all_threads
ggplot(all_threads, aes(x = Thread_Relevancy)) +
  geom_histogram(aes(y = ..count..), binwidth = bin_width, fill = "skyblue", color = "black", alpha = 0.7) + 
  geom_density(aes(y = ..density.. * length(all_threads$Thread_Relevancy) * bin_width), fill = "orange", alpha = 0.4) +  # Scale density to match histogram counts
  labs(title = "Histogram and Density of Thread Relevancy Scores",
       x = "Relevancy",
       y = "Number of Threads") +
  theme_minimal()
```

@@

# Plot the bar graph showing the frequency of each quartile
ggplot(filtered_threads, aes(x = Quartile)) +
  geom_bar(fill = "skyblue", color = "black") +
  geom_text(stat='count', aes(label=..count..), vjust=-0.5) +  # Add labels above bars
  labs(title = "Frequency of Thread Relevancy Quartiles",
       x = "Quartile",
       y = "Frequency") +
  theme_minimal()

@@

# Plot the histogram with density overlay using all_threads
ggplot(filtered_threads, aes(x = Thread_Relevancy)) +
  geom_histogram(aes(y = ..count..), binwidth = bin_width, fill = "skyblue", color = "black", alpha = 0.7) + 
  geom_density(aes(y = ..density.. * bin_width * nrow(all_threads)), fill = "orange", alpha = 0.4) +  # Scale density to match histogram counts
  labs(title = "Histogram and Density of Thread Relevancy Scores",
       x = "Relevancy",
       y = "Number of Threads") +
  theme_minimal()
```
```{r Get Filtered Comments from Filtered Threads}
# Filter threads with only one comment out of filtered threads 
filtered_threads <- filtered_threads %>%
  filter(Number.of.Messages > 1)

@@

output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_influential_authors.html")

tab_df(top_influential_authors,
  file = output_file_path)
```

```{r Calculate and Print Author Influence on Sentiment Scores}
# Filter the all_comments dataset to only include posts by the top 15 influential authors
top_authors_comments <- filtered_comments %>%
  filter(Author %in% top_influential_authors$Author)

# Calculate descriptive statistics for the sentiment scores of influential authors
influential_authors_sentiment_stats <- top_authors_comments %>%
  summarize(
    Min = min(SentimentScore, na.rm = TRUE),
    Max = max(SentimentScore, na.rm = TRUE),
    Range = max(SentimentScore, na.rm = TRUE) - min(SentimentScore, na.rm = TRUE),
    Mean = mean(SentimentScore, na.rm = TRUE),
    Median = median(SentimentScore, na.rm = TRUE),
    SD = sd(SentimentScore, na.rm = TRUE),
    Skewness = skewness(SentimentScore, na.rm = TRUE),
    Kurtosis = kurtosis(SentimentScore, na.rm = TRUE)
  ) %>%
  mutate(Dataset = "Influential Authors")

@@

@@

tab_df(best_matches, ,
  file = output_file_path)
```

@@

ggplot(best_matches, aes(x = factor(Influential_Topic), y = Similarity, fill = factor(Overall_Topic))) +
  geom_bar(stat = "identity") +
  labs(title = "Similarity Between Influential Authors' Topics and Overall Topics",
       x = "Influential Authors' Topic",
       y = "Jaccard Similarity",
       fill = "Best Matching Overall Topic") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

>>>>

# Plot the bar graph showing the frequency of each quartile
ggplot(all_threads, aes(x = Quartile)) +
  geom_bar(fill = "skyblue", color = "black") +
  geom_text(stat='count', aes(label=..count..), vjust=-0.5) +  # Add labels above bars
  labs(title = "Frequency of Thread Relevancy Quartiles",
       x = "Quartile",
       y = "Frequency") +
  theme_bw()

@@

# Plot the histogram with density overlay using all_threads
ggplot(all_threads, aes(x = Thread_Relevancy)) +
  geom_histogram(aes(y = ..count..), binwidth = bin_width, fill = "skyblue", color = "black", alpha = 0.7) + 
  geom_density(aes(y = ..density.. * length(all_threads$Thread_Relevancy) * bin_width), fill = "orange", alpha = 0.4) +  # Scale density to match histogram counts
  labs(title = "Histogram and Density of Thread Relevancy Scores",
       x = "Relevancy",
       y = "Number of Threads") +
  theme_bw()
```

@@

# Plot the bar graph showing the frequency of each quartile
ggplot(filtered_threads, aes(x = Quartile)) +
  geom_bar(fill = "skyblue", color = "black") +
  geom_text(stat='count', aes(label=..count..), vjust=-0.5) +  # Add labels above bars
  labs(title = "Frequency of Thread Relevancy Quartiles",
       x = "Quartile",
       y = "Frequency") +
  theme_bw()

@@

# Plot the histogram with density overlay using all_threads
ggplot(filtered_threads, aes(x = Thread_Relevancy)) +
  geom_histogram(aes(y = ..count..), binwidth = bin_width, fill = "skyblue", color = "black", alpha = 0.7) + 
  geom_density(aes(y = ..density.. * bin_width * nrow(all_threads)), fill = "orange", alpha = 0.4) +  # Scale density to match histogram counts
  labs(title = "Histogram and Density of Thread Relevancy Scores",
       x = "Relevancy",
       y = "Number of Threads") +
  theme_bw()
```
```{r Get Filtered Comments from Filtered Threads}
# Filter threads with only one comment out of filtered threads 
filtered_threads <- filtered_threads %>%
  filter(Number.of.Messages > 1)

@@

# Assuming `top_authors_comments` already filters the dataset for top influential authors
top_authors_comments_summary <- top_authors_comments %>%
  group_by(Author) %>%
  summarize(
    Num_Comments = n(),  # Number of comments
    Num_Threads = n_distinct(Thread.ID),  # Number of unique threads
    Threads_Started = sum(Thread_Relative_CommentID == "CM00004", na.rm = TRUE),  # Number of threads started
    Avg_Sentiment = mean(SentimentScore, na.rm = TRUE),  # Average sentiment score
    Avg_Relevancy = mean(Relevancy, na.rm = TRUE)  # Average relevancy score
  )

# Merge this summary with the original `top_influential_authors` dataframe if needed
influential_authors_metadata <- top_influential_authors %>%
  left_join(top_authors_comments_summary, by = "Author")

# Calculate totals for each numeric column
totals_row <- influential_authors_metadata %>%
  summarize(
    Author = "Total",
    Influence = sum(Influence, na.rm = TRUE),
    Num_Comments = sum(Num_Comments, na.rm = TRUE),
    Num_Threads = sum(Num_Threads, na.rm = TRUE),
    Threads_Started = sum(Threads_Started, na.rm = TRUE),
    Avg_Sentiment = mean(Avg_Sentiment, na.rm = TRUE),  # This is an average; sum might not make sense for sentiment
    Avg_Relevancy = mean(Avg_Relevancy, na.rm = TRUE)   # This is an average; sum might not make sense for relevancy
  )

# Bind the totals row to the bottom of the dataframe
influential_authors_metadata_with_totals <- bind_rows(influential_authors_metadata, totals_row)

# Display the updated table with totals
print(influential_authors_metadata_with_totals)

output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_influential_authors.html")
tab_df(influential_authors_metadata_with_totals, file = output_file_path)
```

```{r Calculate and Print Author Influence on Sentiment Scores}
# Calculate descriptive statistics for the sentiment scores of influential authors
influential_authors_sentiment_stats <- top_authors_comments %>%
  summarize(
    Min = min(SentimentScore, na.rm = TRUE),
    Max = max(SentimentScore, na.rm = TRUE),
    Range = max(SentimentScore, na.rm = TRUE) - min(SentimentScore, na.rm = TRUE),
    Mean = mean(SentimentScore, na.rm = TRUE),
    Median = median(SentimentScore, na.rm = TRUE),
    SD = sd(SentimentScore, na.rm = TRUE),
    Skewness = skewness(SentimentScore, na.rm = TRUE),
    Kurtosis = kurtosis(SentimentScore, na.rm = TRUE)
  ) %>%
  mutate(Dataset = "Dataset Four")

@@

print(best_matches)

@@

tab_df(best_matches, ,
  file = output_file_path)

# Transpose the 'best_matches' dataframe
transposed_best_matches <- as.data.frame(t(best_matches))

# Display the transposed table
print(transposed_best_matches)

output_file_path_transposed <- file.path(output_directory, "images and tables", "table_topic_matches_transposed.html")
tab_df(transposed_best_matches,
  file = output_file_path_transposed)
```

@@

# Create the bar chart and annotate with similarity values
similarity_plot <- ggplot(best_matches, aes(x = factor(Influential_Topic), y = Similarity, fill = factor(Overall_Topic))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = round(Similarity, 2)), 
            position = position_stack(vjust = 0.5), size = 3) + # Add similarity score annotations
  labs(title = "Similarity Between Influential Authors' Topics and Overall Topics",
       x = "Influential Authors' Topic",
       y = "Jaccard Similarity",
       fill = "Best Matching Overall Topic") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

similarity_plot

@@

```{r Distribution of Comments per Newsgroup Plot}
# Load necessary libraries
library(ggplot2)
library(dplyr)

# Calculate the total number of comments per author across all newsgroups
total_comments_by_author <- filtered_comments %>%
  group_by(Author) %>%
  summarise(Total_Comments = n())

# Calculate the number of comments per author per newsgroup
top_authors_by_newsgroup <- filtered_comments %>%
  group_by(Author, newsgroup) %>%
  summarise(Number_of_Comments = n())

# Join the total comments data to the newsgroup data
top_authors_by_newsgroup <- top_authors_by_newsgroup %>%
  left_join(total_comments_by_author, by = "Author")

# Select the top 15 most active authors by total number of comments
top_15_authors <- total_comments_by_author %>%
  arrange(desc(Total_Comments)) %>%
  slice(1:15)  # Ensure only the top 25 authors are selected

# Filter the main data to include only the top 25 authors
top_15_data <- top_authors_by_newsgroup %>%
  filter(Author %in% top_15_authors$Author)

# Create the bar plot using ggplot2 and sort authors in descending order by total number of comments
bar_plot <- ggplot(top_15_data, aes(x = Number_of_Comments, y = reorder(Author, Total_Comments), fill = newsgroup)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 15 Most Active Users in Dataset Three by Newsgroup",
       x = "Number of Comments",
       y = "Author",
       fill = "Newsgroup") +
  theme_bw() +
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 45, hjust = 1))

# Print the plot
print(bar_plot)

# Save the plot to a file
output_file_path <- file.path(output_directory, "images and tables/plot_top_15_most_active_users_by_newsgroup.png")
ggsave(output_file_path, plot = bar_plot, width = 10, height = 6, dpi = 300)
```
```{r Thematic evolution}
library(tidytext)
library(tidyverse)

# Identify top keywords for influential authors
influential_keywords <- top_authors_comments %>%
  unnest_tokens(word, Full.Text) %>%
  anti_join(stop_words) %>%
  count(Author, word, sort = TRUE) %>%
  group_by(Author) %>%
  top_n(5, n) %>%
  ungroup()

# Get the top 20 keywords across all influential authors
top_keywords <- influential_keywords %>%
  group_by(word) %>%
  summarise(total = sum(n)) %>%
  top_n(20, total) %>%
  pull(word)

# Function to calculate keyword prevalence
calculate_keyword_prevalence <- function(df, keywords) {
  df %>%
    unnest_tokens(word, Full.Text) %>%
    filter(word %in% keywords) %>%
    count(Date = floor_date(Date, "month"), word) %>%
    complete(Date, word, fill = list(n = 0)) %>%
    group_by(Date) %>%
    mutate(prevalence = n / sum(n)) %>%
    ungroup()
}

# Calculate keyword prevalence for influential authors and overall discussions
influential_prevalence <- calculate_keyword_prevalence(top_authors_comments, top_keywords)
overall_prevalence <- calculate_keyword_prevalence(filtered_comments, top_keywords)

# Combine the data
combined_prevalence <- bind_rows(
  influential_prevalence %>% mutate(group = "Influential Authors"),
  overall_prevalence %>% mutate(group = "Overall Discussion")
)

# Create the plot
keyword_adoption_plot <- ggplot(combined_prevalence, aes(x = Date, y = prevalence, color = group)) +
  geom_line() +
  facet_wrap(~word, scales = "free_y", ncol = 4) +
  labs(title = "Keyword Adoption Over Time: Influential Authors vs Overall Discussion",
       x = "Date",
       y = "Keyword Prevalence",
       color = "Group") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")

# Print the plot
print(keyword_adoption_plot)

# Save the plot
output_file_path <- file.path(output_directory, "images and tables", "plot_keyword_adoption_over_time.png")
ggsave(output_file_path, plot = keyword_adoption_plot, width = 16, height = 10, dpi = 300)
```

```{r Influence Propogation}
library(igraph)
library(ggraph)
library(tidygraph)
library(dplyr)

# Identify influential authors' threads
influential_threads <- filtered_comments %>%
  filter(Author %in% top_influential_authors$Author) %>%
  select(Thread.ID) %>%
  distinct()

# Create edges based on who commented after influential authors
edges <- filtered_comments %>%
  inner_join(influential_threads, by = "Thread.ID") %>%
  arrange(Thread.ID, Date) %>%
  group_by(Thread.ID) %>%
  mutate(PreviousAuthor = lag(Author)) %>%
  ungroup() %>%
  filter(!is.na(PreviousAuthor), 
         Author != PreviousAuthor,
         PreviousAuthor %in% top_influential_authors$Author) %>%
  select(from = PreviousAuthor, to = Author) %>%
  group_by(from, to) %>%
  summarise(weight = n(), .groups = "drop") %>%
  # Filter for stronger connections
  filter(weight > quantile(weight, 0.25))

# Create graph
graph <- graph_from_data_frame(edges, directed = TRUE)

# Calculate node sizes based on in-degree
node_sizes <- degree(graph, mode = "in")

# Identify top 10 influential nodes
top_nodes <- names(sort(node_sizes, decreasing = TRUE)[1:10])

# Create layout
layout <- create_layout(graph, layout = "fr")

# Create plot
influence_plot <- ggraph(layout) + 
  geom_edge_link(aes(width = weight), alpha = 0.2, arrow = arrow(length = unit(2, 'mm')), end_cap = circle(3, 'mm')) +
  geom_node_point(aes(size = node_sizes, color = name %in% top_influential_authors$Author)) +
  geom_node_text(aes(label = ifelse(name %in% top_nodes, name, "")), repel = TRUE, size = 3) +
  scale_edge_width(range = c(0.1, 2)) +
  scale_size(range = c(1, 10)) +
  scale_color_manual(values = c("TRUE" = "red", "FALSE" = "lightblue")) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Influence Propagation Network",
       subtitle = "Node size represents incoming connections, edge width represents frequency of interaction\nRed nodes are influential authors, labeled nodes are top 10 by incoming connections")

# Print the plot
print(influence_plot)

# Save the plot
output_file_path <- file.path(output_directory, "images and tables", "plot_influence_propagation_network_improved.png")
ggsave(output_file_path, plot = influence_plot, width = 20, height = 16, dpi = 300)
```
